### 2017-02-20 paper.tex
fix vcep archi figure
add chtex to check linter

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at:
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

% Introduction
% First paragraph of paper need be big Alhabet
% \section{Introduction}
% \IEEEPARstart{T}{his}

@@

\section{vCPE System Overview}
Our object is to demonstrate that our vCPE system can help the telco to reduce the Capex and Opex when deploying, maintaining and updating CPE service. This section describes our vCPE system architecture and how we achieve our goal. In the subsection \ref{ssec:service_design}, we will introduce the overview architecture of our virtual CPE Service. Then in subsection \ref{ssec:vcpe_deploy}, we will explain that through the advantages of service architecture, our vCPE system can deploy our service to the customer easily. In the subsection \ref{ssec:vcpe_archi}, we will give details of the whole vCPE system.

\subsection{vCPE Service Design Overview} \label{ssec:service_design}
\begin{figure}[!t]
  \centering
  \includegraphics[width=3in]{./figures/system_overview_v2}
  \caption{vCPE Service Design Architecture}
  \label{fig:service_overview}
\end{figure}
With the concept of SDN-enabled\cite{sdn-enabled} VNFs in Fig. \ref{fig:service_overview}, the network functions have been achived by the synergies between compute and network infrastructures. The former is a VNF controller, mainly responsible for dealing with stateful processing. The latter is a SDN switch, used for stateless processing.

@@

\subsection{Service Deployment Model} \label{ssec:vcpe_deploy}

@@

With architecure mentioned in \ref{ssec:service_design}, we come up with a network function service deployment model.  Because the algorithm and policies handled by computing infrastructures, and the generic network devices, that is, SDN switches, only do stateless processing. The customer only need to buy a general SDN switch at their home gateway and subscribe different NFV controller through our vCPE platform, they will have a different network function service.

In figure \ref{fig:vcpe_deploy} illustrated the service deployment model, each green area is a local network domain of customer. At the gateway of this domain, there's a SDN-enabled switch. The customer can subscribe to our vcpe service through our vcpe dashboard. after subscribing, the vCPE system will create a new docker container, in which running a SDN controller we developed. The customer only need to setup the gateway SDN switch to connect the SDN controller by the OpenFlow protocol, then the switch will handle these service.

\subsection{Architecture of the vCPE system} \label{ssec:vcpe_archi}
\subsubsection{System Overview}
\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/system_overview_v2}
\caption{Service Syetem Overview}
\label{fig:vcpe_system}
\end{figure}

The architecture as shown in Fig \ref{fig:vcpe_system} including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator. The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers running on virtual machines hosting in the cloud using Amazon Web Services (AWS) Data Center also the Infrastructure Controller is a powerful physical blade server running in our laboratory. Each component is introduced in the subsection below.

@@

VNF Controllers contains a SDN controller developed with ryu framework and a remote launcher module. The SDN controller does not have a remote launcher module to remotely execute a SDN controller. We built a light-weight server as a launcher module to resolve the remotely execution issue. The remote launcher module monitor the SDN controller process ID (PID) and properly kill the SDN controller process ID when on demand. When the infrastructure controller once create the container, the remote module will run up initiallly, waiting request from VNF VNF Orchestrator. The details of SDN controller desgin will be presented at section \ref{ssec:vcpe_services}

@@

\section{Virtual CPE Services} \label{ssec:vcpe_services}

>>>>

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf{}
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at:
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle{}
% Introduction
% First paragraph of paper need be big Alhabet
% \section{Introduction}
% \IEEEPARstart{T}{his}

@@

\section{vCPE System Overview}
Our object is to demonstrate that our vCPE system can help the telco to reduce the Capex and Opex when deploying, maintaining and updating CPE service. This section describes our vCPE system architecture and how we achieve our goal. In the subsection\ref{ssec:service_design}, we will introduce the overview architecture of our virtual CPE Service. Then in subsection\ref{ssec:vcpe_deploy}, we will explain that through the advantages of service architecture, our vCPE system can deploy our service to the customer easily. In the subsection\ref{ssec:vcpe_archi}, we will give details of the whole vCPE system.

\subsection{vCPE Service Design Overview}\label{ssec:service_design}
\begin{figure}[!t]
  \centering
  \includegraphics[width=3in]{./figures/service_design_overview}
  \caption{vCPE Service Design Architecture}
\label{fig:service_overview}
\end{figure}
With the concept of SDN-enabled\cite{sdn-enabled} VNFs in Fig.\ref{fig:service_overview}, the network functions have been achived by the synergies between compute and network infrastructures. The former is a VNF controller, mainly responsible for dealing with stateful processing. The latter is a SDN switch, used for stateless processing.

@@

\subsection{Service Deployment Model}\label{ssec:vcpe_deploy}

@@

With architecure mentioned in\ref{ssec:service_design}, we come up with a network function service deployment model.  Because the algorithm and policies handled by computing infrastructures, and the generic network devices, that is, SDN switches, only do stateless processing. The customer only need to buy a general SDN switch at their home gateway and subscribe different NFV controller through our vCPE platform, they will have a different network function service.

In figure\ref{fig:vcpe_deploy} illustrated the service deployment model, each green area is a local network domain of customer. At the gateway of this domain, there's a SDN-enabled switch. The customer can subscribe to our vcpe service through our vcpe dashboard. After subscribing, the vCPE system will create a new docker container, in which running a SDN controller we developed. The customer only need to setup the gateway SDN switch to connect the SDN controller by the OpenFlow protocol, then the switch will handle these service.

\subsection{Architecture of the vCPE system}\label{ssec:vcpe_archi}
\subsubsection{System Overview}
\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/system_overview_v2}
\caption{Service Syetem Overview}
\label{fig:vcpe_system}
\end{figure}

The architecture as shown in Fig\ref{fig:vcpe_system} including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator. The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers running on virtual machines hosting in the cloud using Amazon Web Services (AWS) Data Center also the Infrastructure Controller is a powerful physical blade server running in our laboratory. Each component is introduced in the subsection below.

@@

VNF Controllers contains a SDN controller developed with ryu framework and a remote launcher module. The SDN controller does not have a remote launcher module to remotely execute a SDN controller. We built a light-weight server as a launcher module to resolve the remotely execution issue. The remote launcher module monitor the SDN controller process ID (PID) and properly kill the SDN controller process ID when on demand. When the infrastructure controller once create the container, the remote module will run up initiallly, waiting request from VNF VNF Orchestrator. The details of SDN controller desgin will be presented at section\ref{ssec:vcpe_services}

@@

\section{Virtual CPE Services}\label{ssec:vcpe_services}
\subsection{Multiple Flow Flow Tables}
